General constraints on magic distillation protocols from statistical mechanics

### 2021-05-28 magic_paper.tex
More smoothing of narrative. Deletion of too much explanation. Streamlined. Temp-bound data needs blending next.

Our analysis relies on the discrete Wigner representation of quantum states, in which all states and operations can be described on a discrete phase space~\cite{Ferrie_2008, Okay_2021}. Crucially, we focus on magic states with negativity in their Wigner representation, which is known to be a necessary condition for universality in the state-injection model~\cite{cit:veitch, cit:mari, cit:gottesman, cit:knill, Campbell_2011}. Interestingly, taking a thermodynamic perspective in this context raises a problem, namely it is impossible to define entropies for quasi-distributions. We circumvent this obstacle by making use of a more fundamental tool in thermodynamics -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}. To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of interest to the study of non-classicality in quantum systems.

Through this approach we obtain a range of upper bounds for magic distillation rates. We provide explicit bounds for magic protocols that generate unital channels, as well as bounds that depend on the temperature and Hamiltonian of the system. We find that the thermodynamics in the presence of negativity is surprisingly non-trivial and displays a range of features that do not appear in classical statistical mechanics. 
Finally, we discuss how our approach could be improved and how it can be exploited to construct explicit lower bounds on distillation that take into account physical structure.

@@

A number of magic theories exist, with the central approach of viewing magic states as ``resource'' states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}. One very natural class of free operations are those obtained from Clifford operations, measurements and the ability to discard quantum systems. However, there are also other noteworthy candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.

@@

One of the most prominent magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}

Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.

A range of monotones have been developed in the literature~\cite{cit:howard, Wang_2020, Seddon_2021} and each provides a means to upper bound distillation rates within a particular theory of magic. In this work we shall develop bounds that apply to essentially any reasonable magic theory. The central idea is to apply majorization theory to the quasi-probability distributions of magic states. In the next section, we explain how these majorization constraints relate to the free operations allowed in a theory of magic.

@@

Within the Wigner representation, all negatively represented states are magic states, although in general the converse is not true~\cite{cit:campbell}. However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, so it is natural to focus on the negatively represented magic states. The free states in any magic theory must therefore lie in the set
\begin{equation}
    \Fmax \coloneqq \{ \rho: \W[\bmx]{\rho} \geq 0 \text{ for all } \bmx \in \cal{P}_d\}.
\end{equation}
Our focus is on states with negativity, so the particular choice of free states is not critical for our analysis. The remaining component that defines any magic theory is the set of allowed quantum operations, i.e. the ones that are considered free. The assumption we require on free operations is simply that they send any free state to another free state, meaning that a resource state cannot be created freely, a common assumption among all magic theories.

We can view the Wigner representation $W_{\E}( \y | \x)$ of a quantum channel $\E$ as a transition matrix mapping points $\x \rightarrow \y$, which is consistent with the representation of quantum states, as
\begin{equation}
	W_{\E(\rho)} (\y) = \sum_{\x \in \P_d} W_{\E}( \y | \x) W_\rho(\x),
\end{equation}
for any $\E$ and $\rho$. Now if $\E$ sends all positively represented quantum state to other positively represented quantum states then it can be shown~\cite{Wang_2019} that $W_{\E}(\y |\x)$ must form a stochastic matrix. In particular, all Clifford operations correspond to stochastic matrices in this Wigner representation. However, it is important to note that not all stochastic maps on the phase space correspond to valid quantum operations. In particular, the stochastic maps must respect the symplectic structure of the phase space, which is an additional non-trivial constraint.

In what follows we shall therefore assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set with each state represented by a non-negative Wigner function, while the free operations $\O$ are represented by stochastic maps acting on the discrete phase space.

\section{Magic distillation bounds from majorization theory}
\label{sec:frag}

\nick{repeats intro}
We wish to consider how physical constraints that may be hardware specific, affect magic distillation rates. These are not a priori encoded in the formulation of the magic theory, and constitute additional physical conditions on top of the underlying resource-theoretic accounting. For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.

Our formulation will not consider model-specific limitations, but will still inject broad physical constraints. We proceed by considering fixed-point, or ``equilibrium'', restrictions on the actual operations that are accessible to us. While such restrictions could be viewed as the existence of some non-trivial thermodynamic constraint, they could equally be viewed as encoding a high noise-bias or difficulty in realising a particular quantum gate. We can therefore define the following sub-theory of any magic theory $\R$.
\begin{definition}\label{def:sigmafrag}
   Given a theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the sub-theory $\R_\sigma = (\F, \O_\sigma)$, in which the free operations are 
   \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \},
    \end{equation}
namely those operations that leave the state $\sigma \in \F$ invariant.
\end{definition}
This notion provides a simple way to break up any theory into smaller, more manageable parts that are destinguished by additional physical constraints, illustrated in~\cref{fig:zoo}. Moreover, the union over all fragments returns the parent theory, so we are not discarding any information by breaking up the theory in this way. We make this statement precise as follows.
\begin{theorem}\label{thm:frag}
    Let $\R = (\F, \O)$ be a theory of magic.
Then a transformation $\rho \longrightarrow \tau$ is possible in $\R$ if and only if the transformation $\rho \longrightarrow \tau$ is possible in at least one $\sigma$--fragment of $\R$.
\end{theorem}
\begin{proof}
	The proof is straightforward.
   Suppose the interconversion is possible in a $\sigma$--fragment via some $\E \in \O_\sigma$. But since $\O_\sigma \subseteq \O$ it is also possible in $\R$. Conversely, suppose the transformation is possible in $\R$ via some $\E$ in $\O$. The free states $\F$ are a closed, bounded set and moreover the image of $\F$ under the map $\E$ is in $\F$. By the Brouwer Fixed-Point theorem~\cite{cit:brouwer} this mapping must therefore have a fixed point $\sigma \in \F$. Therefore $\E \in \O_\sigma$ and so the interconversion is possible in this fragment.
\end{proof}

\begin{figure}[t]
    \centering
        \includegraphics[scale=0.3]{figs/operations.pdf}
    \caption{\textbf{Decomposition of a magic theory $\R$ into $\sigma$--fragments.} 
	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) are labelled, with other established magic theories also contained within the yellow regions.
    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
    Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
    Within each $\sigma$--fragment, relative majorisation can be used allowing for a tractable approach towards the study of magic state interconversions.
    }
    \label{fig:zoo}
\end{figure}

\nick{re-write based on new relative majorisation approach}
It is now possible to consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within. Therefore, this route can potentially shed light on how the physics of a protocol constrain distillation rates above and beyond global constraints from the parent resource theory. For example, how does temperature affect distillation bounds? Do isotropic maps have better bounds, or does bias towards some pure stabilizer state provide more freedom?

By introducing this additional structure to a magic theory, we allow for deeper analysis than would be possible at the level of the full parent theory. In particular, the interconversion structure in each fragment can be analysed using tools from single-shot thermodynamics and majorization theory as we discuss in the next section.

@@

We can now show that each magic fragment admits constraints that do not take the form of state monotones.

The question is now whether the sub-theories can be analysed to provide additional insights into magic distillation protocols. An answer can be provided by working in the Wigner representation of a given $\sigma$--fragment. The problem of magic state distillation then becomes that of processing negativity under stochastic maps $W_{\E}( \y |\x)$ that leave a particular quasi-distribution $W_\sigma(\x)$ invariant. However, $\sigma \in \F$ is positively represented, so the sub-theory has an invariant classical probability distribution as a fixed point. This structure allows us to make use of a range of classical tools, and in particular majorization theory.

@@

We can further generalise this to \emph{relative majorization}~\cite{Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017}, defined as an ordering between pairs of vectors so that 
\begin{equation}
	(\p,\r) \succ (\q, \r')
\end{equation}
iff there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\bmd$--majorization when $\r = \r'$.

@@

We wish to apply majorization to describing magic in different fragments at the level of the associated Wigner distributions. However, these are in general quasi-probability distributions and so it is important to detail how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.

Central to the analysis is the notion of a Lorenz curve of a vector $\w \in \mathbb{R}^n$ relative to some other vector $\r \in \mathbb{R}^n$. Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order. Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}$, where $\widetilde{w}_i \coloneqq w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
\begin{equation}
\label{eq:lc}
        (x_k,L_{\w|\r}(x_k)) =\left( \frac{1}{R}\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right),
\end{equation}
where $R\coloneqq \sum_{i=1}^n r_i$ and $\pi$ is the permutation on $n$ objects mapping $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$. The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.
We also observe that the curve contains non-differentiable points, called \emph{elbows} at locations where $\widetilde{\bmw}$ changes value.

If $\w$ and $\r$ are both probability distributions then the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$. The value $L_{\w|\r}(x) = 1$ is a global maximum, attained at the end-point $x=1$. Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it has been shown in~\cite{ruch_mixing_1978} that
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x).
\end{equation}
This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.

However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different. Now the Lorenz curve is no longer monotone increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$. See Figure \ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions. Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality. Since majorization provides a measure of order/disorder this is consistent with the intuition that negativity, for example within the context of entanglement theory or quantum computing, can provide a greater form of order than is possible within classical theory.

@@

However, relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-probability distributions before proceeding with our analysis. This can be done from first principles, but a simpler way is see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization.

More precisely, since the components of $\r$ are strictly positive, there always exists an $\epsilon >0$ such that $\w_\epsilon \coloneqq \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution. We can see that $(\w , \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$, where we choose $\epsilon$ so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions. This equivalence holds because there exists a stochastic map $A$ such that $A \w = \w'$ and $A \r = \r'$ if and only if 
\begin{equation}
A[\epsilon \w + (1-\epsilon) \r] = \epsilon \w' + (1-\epsilon) \r'\mbox{ and } A\r = \r'.
\end{equation}
As mentioned, relative majorization between pairs of distributions occurs if and only if the associated Lorenz curves never cross. Therefore, we can express this condition in terms of the Lorenz curves of the quasi-probability distributions $\w$ and $\w'$ relative to $\r$ and $\r'$ respectively.

As shown in~\cref{lemma:Lorenz_linearity}, the Lorenz curve for any quasi-probability distribution obeys the following linearity condition
\begin{equation}
L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bx,
\end{equation}
for any $a >0$ and $b \in \mathbb{R}$. We now have that
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } (\w_\epsilon , \r) \succ (\w_\epsilon', \r'),
\end{equation}
and also $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x$. However, using the above linearity property of the Lorenz curves we have that
\begin{align}
L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
&\mbox{ if and only if }& \nonumber \\
\epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
\end{align}
The $(1-\epsilon)$ terms cancel on both sides and we get the required relative majorization conditions for the quasi-distributions in terms of their Lorenz curves.

We therefore have that $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w | \r} (x) \ge L_{\w' | \r'}(x)$ for all $x \in [0,1]$ equally applies for the case of $\w,\w'$ being quasi-distributions.

In the next section we discuss the application of majorization to Wigner representations of magic, where the quasi-distribution $W_\rho(x)$ of a magic state can be analysed relative to any Wigner positive free state $W_\sigma(x)$. To our knowledge, the application of majorization to quasi-distributions in  physics has not been considered previously. The caveat here is that relative majorization ranges over stochastic maps that obey a transformation ($A\r = \r'$), while in the case of the Wigner representation there is a stronger restriction that the symplectic structure of the phase space is respected. Therefore, any majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions. This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics? We shall return to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.

@@

Having described how majorization relative to a fiducial distribution can be computed, we now turn to its application within a particular fragment of a magic theory $\R= (\F, \O)$.

@@

\subsection{Magic bounds for unital protocols}
\label{sec:unital}

@@

The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
For the noisy Strange state, the max--thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}. 
Numerical, ``optimal'', bounds $R_{\rm{opt}}$ obtained by considering the entirety of the Lorenz curves have been included in the plot as well, highlighting that the first elbow constraint does not capture the full capabilities of majorization.
Notably, in contrast to the other bounds, $R_{\rm{opt}}$ depends explicitly on the copies $m,n$, rather than their ratio $m/n$, so it is specific to the process.
An interesting open question arises regarding the value of $R_{\rm{opt}}$ as $n,m \rightarrow \infty$, while $m/n$ remains constant.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R$, mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    Numerical bounds $R_{\rm{opt}}$ obtained by full Lorenz curve comparison for some Strange state purification processes with even number of copies $m,n \leq 30$ highlight that the first elbow constraint can be improved.
    }
    \label{fig:distill_bounds}
\end{figure}

In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective. Specifically, we can interpret the stabilizer state $\sigma$, which defines the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.

\newpage
\section{Free energy dependent bounds for magic state distillation protocols}
\label{sec:stab}

>>>>

Our analysis relies on the discrete Wigner representation of quantum systems, in which all states and operations can be described on a discrete phase space~\cite{Ferrie_2008, Okay_2021}. Crucially, we focus on magic states with negativity in their Wigner representation, which is known to be a necessary condition for universality in the state-injection model~\cite{cit:veitch, cit:mari, cit:gottesman, cit:knill, Campbell_2011}. Interestingly, taking a statistical mechanical perspective in this context raises a problem, namely it is impossible to define entropies for quasi-distributions. We circumvent this obstacle by making use of a more fundamental tool in thermodynamics and information theory -- majorization theory~\cite{cit:marshall, Veinott_1971, Ruch_1976}. To our knowledge majorization of quasi-distributions has not been considered in quantum physics before, and therefore our analysis is also of interest to the study of non-classicality in quantum systems.

Through this approach we obtain a range of upper bounds for magic distillation rates. We provide explicit bounds for magic protocols that generate unital channels, as well as bounds that depend on the temperature and Hamiltonian of the system. We find that the thermodynamic ordering in the presence of negativity is non-trivial and displays a range of features that, unsurprisingly, do not appear in classical statistical mechanics. 
Finally, we discuss how our approach could be improved and how it can be exploited to construct explicit lower bounds on distillation that take into account physical structure.

@@

A number of magic theories exist, with the central approach of viewing magic states as computational resource states with respect to a natural class of quantum operations that are considered free~\cite{Gour_2019}. One very natural class of free operations are those obtained from Clifford operations, measurements and the ability to discard quantum systems. However, there are also other noteworthy candidates~\cite{cit:ahmadi, cit:seddon, Wang_2019}.

@@

One prominent magic monotone is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}

Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$.} magic monotone, and the fact that it is non-increasing under free operations provides a constraint on magic state interconvertibility.

In this work we shall develop bounds that apply to essentially any reasonable magic theory. The central idea is to apply majorization theory to the quasi-probability distributions that arise for magic states. We begin in the next section by explaining how majorization relates to the free operations in a theory of magic.

@@

Within the Wigner representation, all negatively represented states are magic states, although in general the converse is not true~\cite{cit:campbell}. However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, so it is natural to focus on the negatively represented magic states. The free states in any magic theory are assumed to lie in the set
\begin{equation}
    \Fmax \coloneqq \{ \rho: \W[\bmx]{\rho} \geq 0 \text{ for all } \bmx \in \cal{P}_d\}.
\end{equation}
Our focus is on states with negativity, so the particular choice of free states is not critical for our analysis. The remaining component that defines any magic theory is the set of allowed quantum operations, i.e. the ones that are considered free within the theory. The most basic assumption we require on free operations is that they send any free state to another free state, meaning that a resource state cannot be created freely, a common assumption among all magic theories.

Any magic state protocol will correspond to a quantum channel $\E$, and admits a Wigner representation $W_{\E}( \y | \x)$ that can be viewed as a transition matrix mapping phase space points $\x \rightarrow \y$. The representation obeys the relation 
\begin{equation}
	W_{\E(\rho)} (\y) = \sum_{\x \in \P_d} W_{\E}( \y | \x) W_\rho(\x),
\end{equation}
for any $\E$ and $\rho$. Now if any magic protocol will send free states to free states, and so $\E$ sends all positively represented quantum state to other positively represented quantum states. In such cases, it can be shown~\cite{Wang_2019} that $W_{\E}(\y |\x)$ must form a stochastic matrix. In particular, all Clifford operations correspond to stochastic matrices in this Wigner representation.

However, it is important to note that this is not one-to-one. Not all stochastic maps on the phase space correspond to valid quantum operations. The reason is that the stochastic maps must also respect the symplectic structure of the phase space, which is an additional non-trivial constraint.

In what follows we shall assume that we have a magic theory $\R = (\F, \O)$ in which the free states $\F$ form a closed set and are represented by a non-negative Wigner functions, while the free operations $\O$ are stochastic maps in the Wigner representation. To aid our analysis of magic in this phase space setting we shall make use of majorization theory, which we describe in the next section.

@@

@@

In fact, we can further generalise to \emph{relative majorization}~\cite{Ruch_1976, ruch_mixing_1978, Renes_2016, Buscemi_2017}, defined as an ordering between pairs of vectors so that 
\begin{equation}
	(\p,\r) \succ (\q, \r')
\end{equation}
iff there is a stochastic map $A$ such that $A\r = \r'$ and $A\p = \q$. We retrieve $\bmd$--majorization when $\r = \r'$.

@@

Our analysis applies majorization to magic states at the level of the associated Wigner distributions. However, these are in general quasi-probability distributions and so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions.

Central to the analysis is the notion of a Lorenz curve of a vector $\w \in \mathbb{R}^n$ relative to some other vector $\r \in \mathbb{R}^n$. Given a vector $\w$ we define $\w^\downarrow$ to be the re-arrangement of the components of $\w$ into decreasing order. Given two $n$--component vectors $\w$ and $\r$, we first define $\widetilde{\w}$, where $\widetilde{w}_i \coloneqq w_i/r_i$, as the vector of component-wise ratios between $\w$ and $\r$.
We can now define the \emph{Lorenz curve} of $\w$ relative to $\r$, denoted $L_{\w|\r}(x)$, as the piece-wise linear function that passes through $(0,0)$ and the $n$ points
\begin{equation}
\label{eq:lc}
        (x_k,L_{\w|\r}(x_k)) =\left( \frac{1}{R}\sum_{i=1}^k r_{\pi(i)}, \sum_{i=1}^k w_{\pi(i)} \right),
\end{equation}
where $R\coloneqq \sum_{i=1}^n r_i$ and $\pi$ is the permutation on $n$ objects mapping $\widetilde{\w}$ to $\widetilde{\w}^{\downarrow}$. The form of this requires that $\r$ has no zero components, which we shall assume without loss of generality as in any physical situation the rank of a quantum state is not an operationally meaningful quantity.

In the usual case where $\w$ and $\r$ are both probability distributions the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$. The value $L_{\w|\r}(x) = 1$ is a global maximum. Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it can be shown~\cite{ruch_mixing_1978} that
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
\end{equation}
for all $x \in [0,1]$.
This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.

However, if $\w$ is a \emph{quasi-probability} distribution with negative values, and $\r$ a regular probability distribution things are different. Now the Lorenz curve is no longer monotone increasing, but is a concave function that breaks through the $L_{\w|\r}(x) = 1$ barrier at an interior point and attains some non-trivial maximum $L_\star$ above the value $1$, before decreasing monotonically to $L_{\w|\r}(x)= 1$ at the end-point $x=1$. See Figure \ref{fig:lcs} for examples of non-monotonic Lorenz curves for quasi-distributions. Within quantum theory, the breaking of this barrier is associated with the degree of non-classicality. Since majorization provides a measure of order/disorder this is consistent with the intuition that negativity, for example within the context of quantum optics or quantum computing, can provide a greater form of order than is possible within classical theory.

@@

However, relative majorization is usually considered for probability distributions, so we need to verify that the same Lorenz curve conditions apply to quasi-probability distributions before proceeding with our analysis. This can be done from first principles, but a simpler way is see that this holds is to reduce to the problem of genuine distributions by first `masking' the negativity in the quasi-probability distribution $\w$ using the reference distribution $\r$ and then applying the conditions for relative majorization. This negativity masking then gives the following result.

\begin{lemma} Let $\w \in \mathbb{R}^n,\w'\in \mathbb{R}^m$ be quasi-distributions, and let $\r \in \mathbb{R}^n, \r' \in \mathbb{R}^m$ be probability distributions with non-zero components. Then $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w|\r}(x) \ge L_{\w |\r}(x)$ for all $x \in [0,1]$.
\end{lemma}

 \begin{proof}
Since the components of $\r$ are strictly positive, there always exists an $\epsilon >0$ such that $\w_\epsilon \coloneqq \epsilon \w + (1-\epsilon) \r$ is a genuine probability distribution. A similar result holds for $\w'$ and $\r'$ and we choose $\epsilon$ sufficiently small so that both $\w_\epsilon$ and $\w_\epsilon'$ are probability distributions. We now have that $(\w , \r) \succ (\w', \r')$ if and only if $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$. This equivalence holds because there exists a stochastic map $A$ such that $A \w = \w'$ and $A \r = \r'$ if and only if 
\begin{equation}
A[\epsilon \w + (1-\epsilon) \r] = \epsilon \w' + (1-\epsilon) \r'\mbox{ and } A\r = \r'.
\end{equation}
In terms of a Lorenz curve condition we have that $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x \in [0,1]$. 
However, as we show in the Appendices (\cref{lemma:Lorenz_linearity}), the Lorenz curve for any quasi-probability distribution obeys the relation
\begin{equation}
L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bx,
\end{equation}
for any $a >0$ and $b \in \mathbb{R}$. This relation implies that
\begin{align}
L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
&\mbox{ if and only if }& \nonumber \\
\epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
\end{align}
Finally, the $(1-\epsilon)x$ terms cancel on both sides and we get the required relative majorization conditions that $(\w, \r) \succ (\w', \r')$ if and only if $L_{\w | \r} (x) \ge L_{\w' | \r'}(x)$ for all $x \in [0,1]$, as required.
\end{proof}

With all the necessary theory in place, we now turn to magic distillation protocols.

\newpage
\section{Magic distillation bounds from majorization}
\label{sec:frag}

We can now consider how physical constraints that may be hardware specific, affect magic distillation rates. These are not a priori encoded in the formulation of the magic theory, and constitute additional physical conditions on top of the underlying resource-theoretic accounting. For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.

 In Section \ref{sec:stab} we shall focus on the energetic costs of a protocol, that are defined due to the specific Hamiltonian that the system possesses. However, before that, in this section we encode physical constraints at a more abstract level in terms of the fixed-point structure of  the actual operations that are accessible to us. We show that any magic theory can always be decomposed in terms of `sub-theories' with a particular fixed-point structure. This section therefore exploits $\mathbf{d}$--majorization, while in Section \ref{sec:stab} we drop the requirement of fixed-points and instead use the full relative majorization relation.

 We begin by defining the following sub-theory of any magic theory $\R$.
\begin{definition}\label{def:sigmafrag}
   Given a theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the sub-theory $\R_\sigma = (\F, \O_\sigma)$, in which the free operations are 
   \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \},
    \end{equation}
namely those operations that leave the state $\sigma \in \F$ invariant.
\end{definition}
This notion provides a simple way to break up any theory into smaller, more manageable parts that are destinguished by additional physical constraints, illustrated in~\cref{fig:zoo}. Moreover, the union over all fragments returns the parent theory, so we are not discarding any information by breaking up the theory in this way. We make this statement precise as follows.
\begin{theorem}\label{thm:frag}
    Let $\R = (\F, \O)$ be a theory of magic.
Then a transformation $\rho \rightarrow \tau$ is possible in $\R$ if and only if the transformation $\rho \rightarrow \tau$ is possible in at least one $\sigma$--fragment of $\R$.
\end{theorem}
The proof of this is straightforward.
\begin{proof}
   Suppose the interconversion is possible in a $\sigma$--fragment via some $\E \in \O_\sigma$. But since $\O_\sigma \subseteq \O$ it is also possible in $\R$. Conversely, suppose the transformation is possible in $\R$ via some $\E$ in $\O$. The free states $\F$ are a closed, bounded set and moreover the image of $\F$ under the map $\E$ is in $\F$. By the Brouwer Fixed-Point theorem~\cite{cit:brouwer} this mapping must therefore have a fixed point $\sigma \in \F$. Therefore $\E \in \O_\sigma$ and so the interconversion is possible in this fragment.
\end{proof}

\begin{figure}[t]
    \centering
        \includegraphics[scale=0.3]{figs/operations.pdf}
    \caption{\textbf{Decomposition of a magic theory $\R$ into $\sigma$--fragments.} 
	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) are labelled, with other established magic theories also contained within the yellow regions.
    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
    Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
    Within each $\sigma$--fragment, relative majorisation can be used allowing for a tractable approach towards the study of magic state interconversions.
    }
    \label{fig:zoo}
\end{figure}
It is now possible to consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within.

@@

@@

\subsection{Magic distillation bounds for unital protocols}
\label{sec:unital}

@@

The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
For the noisy Strange state, the max--thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}. 
Numerical, ``optimal'', bounds $R_{\rm{opt}}$ obtained by considering the entirety of the Lorenz curves have been included in the plot as well, highlighting that the first elbow constraint does not capture the full capabilities of majorization.
Notably, in contrast to the other bounds, $R_{\rm{opt}}$ depends explicitly on the copies $m,n$, rather than their ratio $m/n$, so it is specific to the process.
An interesting open question arises regarding the value of $R_{\rm{opt}}$ as $n,m \rightarrow \infty$, while $m/n$ remains constant.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint $R$, mana $\M$ and max--thauma $\theta_{\rm{max}}$ are plotted for $\epsilon' = 0$, up to error $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    Numerical bounds $R_{\rm{opt}}$ obtained by full Lorenz curve comparison for some Strange state purification processes with even number of copies $m,n \leq 30$ highlight that the first elbow constraint can be improved.
    }
    \label{fig:distill_bounds}
\end{figure}

In the next section we leave fragments behind, and instead use the full structure of relative majorization to obtain bounds that incorporate energetic aspects of a magic state protocol.

\newpage
\section{Temperature-dependent bounds for magic state distillation protocols}
\label{sec:stab}
